Empirical Evaluation of eval in R

### 2020-08-19 inst/analysis/analysis_stable.Rmd
Type classification for expr_resolved

```{r not_unchanged_eval}
changed_evals <- eval_calls %>% mutate(changed =  fct_collapse(expr_expression_type, base_types = c("LANGSXP", "EXPRSXP", "SYMSXP", "PROMSXP", "BCODESXP"))) %>% count(changed) %>% mutate(per_cent = n / nb_eval_calls * 100 ) 
```

@@

- assignments
- reading (in a data frame, a vector)
- parsing
- defusing (`quote` and so on)
- conversion or creation of new values
- building calls and calling
- working with environments
- class assignments, reads and definitions
- building logical values
- formula
- meta programming on functions (getting access to the body of the function, to the call stack)
- 'NA' corresponds to no function calls (or that it was not deparsed successfully)

@@

>>>>

```{r not_unchanged_eval}
changed_evals <- eval_calls %>% mutate(changed =  fct_collapse(expr_expression_type, lang_types = c("LANGSXP", "EXPRSXP", "SYMSXP", "PROMSXP", "BCODESXP"), other_level = "other_types")) %>% count(changed) %>% mutate(per_cent = n / nb_eval_calls * 100 ) 
```

@@

- assignments
- reading (in a data frame, a vector)
- parsing
- defusing (`quote` and so on)
- conversion or creation of new values
- building calls and calling
- working with environments
- class assignments, reads and definitions
- building logical values
- formula
- meta programming on functions (getting access to the body of the function, to the call stack)
- 'NA' corresponds to no function calls (or that it was not parsed successfully)

@@

### For resolved `expr`

We can do the same for resolved expressions:

```{r types_resolved}
per_expr_resolved_type <- eval_calls %>% count(expr_resolved_type)
```

```{r}
 per_expr_resolved_type %>% mutate(per_cent = n / nb_eval_calls * 100 ) %>% arrange(desc(n)) %>% knitr::kable()
```

```{r}
per_expr_resolved_type %>% ggplot() +
  geom_col(aes(x = fct_reorder(expr_resolved_type, n), y = n)) +
  scale_y_sqrt() + 
  coord_flip() +
  labs(title = "Calls per type", y = "n", x = "type" ) 
```

There is a much larger variety of types for the resolved expressions.

```{r not_unchanged_resolved_eval}
changed_resolved_evals <- eval_calls %>% mutate(changed =  fct_collapse(expr_resolved_type, lang_types = c("LANGSXP", "EXPRSXP", "SYMSXP", "PROMSXP", "BCODESXP"), other_level = "other_types")) %>% count(changed) %>% mutate(per_cent = n / nb_eval_calls * 100 ) 
```

We can remove `eval` and leave there the expression in `r changed_resolved_evals[2, "per_cent"][[1]]`% of the eval calls (i.e. `r changed_resolved_evals[2, "n"][[1]]`).
